API design for machine learning: experiences from scikit-learn

### 2014-02-18 paper.tex
less advertising/implementation stuff

\sklearn is designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries
\citep{oliphant2007python, vanderwalt2011}.
NumPy augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy extends it further with common numerical operations,
either by implementing these in Python/NumPy
or by wrapping existing C/C{}\verb!++!/Fortran code.
IPython \citep{perez2007ipython} and Matplotlib \citep{hunter2007matplotlib}
complement SciPy to provide a \textsc{matlab}-like working environment
suited for scientific use.

Since 2007, \sklearn has been developed by more than a dozen
core developers, mostly researchers in fields ranging from
neuroscience to astrophysics. It also benefits
from occasional contributors proposing small bugfixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
Documentation and examples are required for all features,
and major changes must pass code review by at least two other
developers.

@@

To facilitate the installation of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
Visualization functionality uses Matplotlib \citep{hunter2007matplotlib}
and Graphviz \citep{gansner2000},
but neither is required to perform machine learning or prediction.
When feasible, external libraries are integrated into the codebase.
In particular, \sklearn includes modified versions of the C{}\verb!++! libraries
\textsf{LIBSVM} and \textsf{LIBLINEAR} \citep{chang2011libsvm,fan2008}.

>>>>

\sklearn is designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries
\citep{oliphant2007python, vanderwalt2011}.
NumPy augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy extends it further with common numerical operations,
either by implementing these in Python/NumPy
or by wrapping existing C/C{}\verb!++!/Fortran code.

@@

To facilitate the installation of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
